---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2023

<!-- badges: start -->
[![R-CMD-check](https://github.com/YRblack/bis620.2023/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/YRblack/bis620.2023/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/YRblack/bis620.2023/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/YRblack/bis620.2023/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The bis620.2023 package is developed as an extension of our midterm project in BIS 620 Fall 2023. This package is structured to encompass a comprehensive suite of functions and datasets used in our midterm project.

Core Functionality: The core of the bis620.2022 lies the `start_shiny` function. This function serves as a gateway to an interactive Shiny application, designed to provide an user-friendly interface for exploring the extensive data from clinicaltrials.gov trials. The application is tailored to facilitate in-depth analysis and visualization of clinical trial data.

## Installation

You can install the development version of bis620.2023 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("YRblack/bis620.2023")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bis620.2023)
accel |> 
  head(100) |> 
  plot_accel()
```

